---
output: github_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hoplon

<!-- badges: start -->
<!-- badges: end -->

The goal of hoplon is to provide a light-weight and tidy interface to human phenotype ontology (HPO) terms. It provides functions to make working with clinical deep computational phenotyping data more convenient.

## Installation

You can install the development version of hoplon like so:

``` r
# install.packages("devtools")
devtools::install_github("christianbosselmann/hoplon")
```

## Example

This basic examples takes a tibble with a column term of HPO IDs, propagates them to their ancestors and returns the term description for each ancestor. Note that functions return character vectors as column lists - unnest them if needed.

```{r example}
library(tidyverse)
library(hoplon)
data <- tibble(term = c("HP:0011146", "HP:0012736", "HP:0000717"))
data %>%
  mutate(description_term = hoplon::describe(term)) %>%
  mutate(ancestors = hoplon::ancestors(term)) %>% 
  unnest(cols = ancestors) %>%
  mutate(description_ancestors = hoplon::describe(ancestors)) 
  
```
